\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{mathpazo} % Use the Palatino font by default
\usepackage[backend=bibtex, natbib=true]{biblatex}
\usepackage[autostyle=true]{csquotes}
\usepackage{float}
\usepackage{graphics}
\usepackage{tikz}
\usepackage{scalerel,amssymb}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{dirtree}


\usepackage{tikz}
\usetikzlibrary{positioning,shapes}

\addbibresource{references.bib}
\graphicspath{{figures/}} 

% some commands
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{ \node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
\newcommand{\kuka}{\textrm{Kuka LBR IIWA}}

\newcommand{\kt}{kinesthetic}
\newcommand{\te}{teleoperation}
\newcommand{\Kt}{Kinesthetic}
\newcommand{\Te}{Teleoperation}

\newcommand{\rep}{$ 3 $}
\newcommand{\nobj}{$ 3 $}

\newcommand{\smallusers}{\textbf{LBU}}
\newcommand{\bigusers}{\textbf{HBU}}
\newcommand{\regular}{\textbf{RP}}
\newcommand{\casual}{\textbf{RP}}

%	MARGIN SETTINGS

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=3cm, % Inner margin
	outer=3cm, % Outer margin
	%bindingoffset=.5cm, % Binding offset
	top=2cm, % Top margin
	bottom=2cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

\setlength\parindent{0pt}

%	THESIS INFORMATION

\thesistitle{Towards an optimal teaching method for industrial assembly tasks using collaborative robots: teleoperation vs kinesthetic.}
\supervisor{Dr. Diego \textsc{Dall'Alba}}

\degree{Master of Science in Computer Science}
\author{Michele \textsc{Penzo}}
\keywords{}
\university{\href{https://www.univr.it/en/home}{University of Verona}}
\department{\href{https://www.di.univr.it/?lang=en}{Department of Computer Science}}
\group{\href{https://www.icelab.di.univr.it/}{ICE Laboratory}}
\faculty{ }

\AtBeginDocument{
	\hypersetup{pdftitle=\ttitle}
	\hypersetup{pdfauthor=\authorname}
	\hypersetup{pdfkeywords=\keywordnames}
}

%	BEGIN DOCUMENT

\begin{document}
	
	\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages
	\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content
	
	%	TITLE PAGE
	\begin{titlepage}
		\begin{center}
			
			\vspace*{.06\textheight}
			{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
			\textsc{\Large Master Thesis}\\[1.5cm] % Thesis type
			
			\HRule \\[0.4cm] % Horizontal line
			{\LARGE \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
			\HRule \\[2.5cm] % Horizontal line
			
			\begin{minipage}[t]{0.4\textwidth}
				\begin{flushleft} \large
					\emph{Candidate:}\\
					\href{mailto:michelepenzo@outlook.it}{\authorname}\\ % Author name
					VR439232
				\end{flushleft}
			\end{minipage}
			\begin{minipage}[t]{0.4\textwidth}
				\begin{flushright} \large
					\emph{Supervisor:} \\
					\href{https://www.di.univr.it/?ent=persona&id=6321&lang=en}{\supname} % Supervisor name
				\end{flushright}
			\end{minipage}\\[3cm]
			
			\vfill
			
			\groupname\\\deptname\\[2cm] % Research group name and department name
			
			\vfill
			{\large Academic Year 2019--2020}\\[2cm] % Date
			
			\vfill
		\end{center}
	\end{titlepage}
	
	%	ABSTRACT PAGE
	\begin{abstract}
		\addchaptertocentry{\abstractname} % Add the abstract to the table of contents

		\selectlanguage{english}

		The advent of Industry 4.0 has significantly increased the adoption of robotics in all industrial domains. In Industry 4.0 scenario, collaborative robots are widely used as they are simpler to install (i.e., safe human interaction) and they provide advanced functionalities essential for the automation of complex tasks. This steady increase in the number of installed robots has introduced new challenges, such as being able to reprogram them quickly and easily. 
		Various methodologies have been proposed for rapid robot reprogramming. However, it is challenging to propose a programming method able to provide an intuitive access to advance collaborative robots functionalities. In this thesis, we propose to employ a common input device used in the videogame field for the teleoperated programming of collaborative robots. We compared the proposed programming approach with one of the most used method for programming collaborative robots: \kt{} teaching. 
		The experimental evaluation is based on a user experiments to find the most user-friendly and intuitive way to program assembly task. We have considered different characteristic of the users, and the obtained results demonstrate that the physical characteristics and the confidence with the input device used for \te{} affect the overall performance in teaching of an assembly task.\\[2cm]

		\selectlanguage{italian}	% set language only for this paragraph
		
		L'avvento di Industria 4.0 ha notevolmente favorito l'utilizzo dei robot in tutti i campi industriali. In questo scenario, i robot collaborativi sono ampiamente utilizzati in quanto sono più semplici da installare (e.g., interazione umana sicura) e forniscono funzionalità avanzate essenziali per l'automazione di attività complesse.
		Questo costante aumento del numero di robot ha introdotto nuove sfide, come la possibilità di riprogrammarli rapidamente e facilmente. Sono state proposte varie metodologie per la riprogrammazione rapida dei robot.
		Tuttavia, è difficile proporre un metodo di programmazione in grado di fornire un accesso intuitivo alle funzionalità avanzate dei robot collaborativi.
		In questo lavoro di tesi si propone di utilizzare un comune dispositivo di input utilizzato nel campo dei videogiochi per la programmazione tramite teleoperazione di robot collaborativi.
		È stato confrontato l'approccio di programmazione proposto con uno dei metodi più utilizzati per la programmazione di robot collaborativi: l'insegnamento cinestetico.
		La valutazione sperimentale, basata su un esperimento condotto su un campione di utenti, è stata svolta per individuare il modo più facile e intuitivo per programmare l'attività di assemblaggio.
		Sono state prese in considerazione diverse caratteristiche degli utenti e i risultati ottenuti dimostrano che le caratteristiche fisiche e la confidenza con il dispositivo di input utilizzato influenzano le prestazioni complessive nell'insegnamento di un'attività di assemblaggio.
		
	\end{abstract}
	
	%	ACKNOWLEDGEMENTS
	%\begin{acknowledgements}
	%\addchaptertocentry{\acknowlabstract edgementname} % Add the acknowledgements to table of contents
	%\ldots
	%\end{acknowledgements}
	
	%	LIST OF CONTENTS
	\tableofcontents 
	\listoffigures
	\listoftables	

	%	ABBREVIATIONS
	\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
	\textbf{PBD} & \textbf{P}rogramming \textbf{B}y \textbf{D}emonstration\\
	\textbf{LBR} & \textbf{L}eicht \textbf{B}au \textbf{R}oboter\\
	\textbf{IIWA}& \textbf{I}ntellingent \textbf{I}ndustrial \textbf{W}ork \textbf{A}ssistant\\
	\textbf{ROS} & \textbf{R}obot \textbf{O}perating \textbf{S}ystem\\
	\textbf{KRC} & \textbf{K}uka \textbf{R}obot \textbf{C}ontroller\\
	\textbf{EE}  & \textbf{E}nd \textbf{E}ffector\\
	\textbf{KT}  & \textbf{K}inesthetic \textbf{T}eaching\\
	\textbf{TT}  & \textbf{T}eleoperation \textbf{T}eaching\\
	\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex\\
	\textbf{LBU} & \textbf{L}ow \textbf{B}MI \textbf{U}sers\\
	\textbf{HBU} & \textbf{H}igh \textbf{B}MI \textbf{U}sers\\
	\textbf{RP}  & \textbf{R}egular \textbf{P}layers\\
	\textbf{CP}  & \textbf{C}asual \textbf{P}layers\\
		
	\end{abbreviations}
	
	
	%	THESIS CONTENT - CHAPTERS
	
	\mainmatter % Begin numeric (1,2,3...) page numbering
	\pagestyle{thesis}
	
	\selectlanguage{english}	% set language
	
	\include{chapters/introduction}
	\include{chapters/state_of_the_art}
	\include{chapters/materials_methods}
	\include{chapters/preliminary_experiments}
	\include{chapters/experiment}
	\include{chapters/results_analysis}
	\include{chapters/results_discussion}
	\include{chapters/conclusion}
	
	%	BIBLIOGRAPHY
	\printbibliography[heading=bibintoc, title=References]
	
\end{document}  